Data Management for LSST Special Programs

### 2024-03-27 sec_proc.tex
remove timescales from S.4.3.2

For example, Special Processing for the DDF data products might include:
\begin{itemize}
\item nightly-coadded images (24 h)
\item nightly-coadded difference images (24 h)
\item {\tt DiaSource}- and {\tt DiaObject}-like catalogs for the nightly-coadds (24 h)
\item deeply-coadded images (all images to date; yearly)
\item templates for the nightly-coadded difference images (yearly)
\item {\tt Source}- and {\tt Object}-like catalogs for the nightly-coadded and deeply-coadded images (yearly)
\end{itemize}

>>>>

For example, Special Processing for the DDF data products might include:
\begin{itemize}
\item nightly-coadded images
\item nightly-coadded difference images
\item {\tt DiaSource}- and {\tt DiaObject}-like catalogs for the nightly-coadds
\item deeply-coadded images
\item templates for the nightly-coadded difference images
\item {\tt Source}- and {\tt Object}-like catalogs for the nightly-coadded and deeply-coadded images
\end{itemize}

The release of nightly-coadded or difference images is subject to the 80-hour embargo.
The timescales for updating catalogs based on the nightly-coadds could be daily
or on another intermediate timescale; this is left to the discretion of Rubin Data Management.
